---
title: "Difference in Differences Warmup"
output: html_notebook
---

In 1992, the minimum wage in New Jersey was increased from \$4.25 to \$5.05. In nearby Pennsylvania, the minimum wage stayed the same.

In order to determine whether this change affected employment, data about the number of employees at fast food restaurants was collected before and after the change. You've been provided this data.

```{r}
library(tidyverse)

employment <- read_csv("../data/employment.csv")
```

In the state column, 0 corresponds to Pennsylvania and 1 corresponds to New Jersey.

**Part 1:** In the state column, replace 0 with "PA" and 1 with "NJ". Hint: You can use the case_when function for this. 
```{r}
employment <- employment |> 
  mutate(state = case_when(state == 0 ~ 'PA',
            state == 1 ~ 'NJ'))

employment
```


```{r}
employment <- employment |> 
  mutate(post_pre = total_emp_nov - total_emp_feb)

employment
```
**Part 2:** Find the average number of employees split out by state and month.
```{r}
tibblish <- employment |> 
  group_by(state) |> 
  summarize(mean(total_emp_feb), 
            mean(total_emp_nov), 
            mean(post_pre))

tibblish
```

```{r}
tibblish |> 
  add_row(state = 'NJ-PA',
          `mean(total_emp_feb)` = 20.43058 - 23.38000,
          `mean(total_emp_nov)` = 20.89725 - 21.09667,
          `mean(post_pre)` = 0.4666667 - (-2.2833333))
```

```{r}
tibblish |> 
  arrange(desc(state)) |> 
  mutate(diff(`mean(post_pre)`))
```

**Part 4:** Create a plot showing the averages before and after for each group. You should color your plot by the group.
Hint: You may need to pivot your data so that the averages are all contained in one column.

```{r}
tibblish |> 
  pivot_longer(cols = c(`mean(total_emp_feb)`,
                        `mean(total_emp_nov)`, 
                        `mean(post_pre)`)) |> 
  filter(state %in% c('NJ', 'PA'), name != 'mean(post_pre)') |> 
  ggplot(aes(x=name, y=value, fill = state)) +
  geom_col(position = 'dodge')
```
```{r}
tibblish |> 
  pivot_longer(cols = c(`mean(total_emp_feb)`,
                        `mean(total_emp_nov)`, 
                        `mean(post_pre)`)) |> 
  filter(state %in% c('NJ', 'PA'), name != 'mean(post_pre)') |> 
  ggplot(aes(x=name, y=value, color = state, group = state)) +
  geom_point() +
  geom_line()
```

**Part 5:** Set up a regression model to estimate the effect of the minimum wage increase on the average number of employees. 
Hint: You'll need to pivot the data so that the employment numbers are all in one column.
What is the estimate for the effect? Is it statistically significant?


```{r}
emp_model <- employment |> 
  select(-post_pre) |> 
  pivot_longer(cols = c(total_emp_feb, total_emp_nov)) |> 
  mutate(pre_post = if_else(name == "total_emp_feb", "pre", "post")) 

```


```{r}
  glm(value ~ pre_post + state, data = emp_model)
```
```{r}
lm(value ~ state + pre_post + state:pre_post, data = emp_model)
```

